Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-10 Report/mse_formulation.tex
halfcooked

In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable \ac{SINR} by using the receivers designed with the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. \review{Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as}
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. \review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}

>>>>

In this, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals as shown in \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. \review{Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as}
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. \review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}

### 2015-04-10 Report/wsrm_formulation.tex
halfcooked

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let us define a function, 
\begin{equation}
f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
\end{equation}
where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation. Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. \review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as the \ac{SCA} approach in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}

>>>>

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let us define a function, 
\begin{equation}
f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
\end{equation}
where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation. Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. \review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}
